---  
title: "SISCAL OM fit report"
geometry: letterpaper
nocaption: false
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage[table]{xcolor}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{caption}
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
always_allow_html: yes
params:
  rootDir: "~/Work/code/models/stockAssessment/SISCA/Outputs/fits/fit_04022020101311"
  RdataFile: "fit_04022020101311.RData"
  prevRep: "scal.rep"
output: 
  pdf_document:
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: ~/Work/write/templates/tex/TandF.latex
  html_document:
    self_contained: true
    toc: true
    toc_depth: 2
    toc_float: true
    df_print: kable
    keep_md: false
  word_document:
    df_print: kable
    reference_docx: /Users/sdnjohnson/Work/write/templates/docx/basic.docx
  bookdown::pdf_document2:
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: ~/Work/write/templates/tex/TandF.latex
    fig_width: 7
    fig_height: 6
  bookdown::html_document2:
    self_contained: true
    df_print: kable
    keep_md: false
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: false
  bookdown::word_document2:
    df_print: kable
    reference_docx: /Users/sdnjohnson/Work/write/templates/docx/basic.docx
---

# Data Scenario and Model Hypothesis

```{r, setup, message=FALSE, warning=FALSE, include=FALSE, echo = FALSE}

# I usually load my libraries up front to keep things organized
library( bookdown )
library( knitr )
library( kableExtra )
library( dplyr )
library( stringr )
library( tidyverse )
library( here )
library( tmbstan )
library( rstan )

knitr::opts_chunk$set(  fig.pos = 'p',
                        out.width = '100%', dpi=300, 
                        root.dir = params$rootDir,
                        message = FALSE, warning = FALSE, echo = FALSE,
                        fig.width = 8, fig.height = 6 )

options(warn = -1)

source(here("SISCAtools.R"))
source(here("SISCAplots.R"))
source(here("SISCAfuns.R"))
source(here("SISCArefPts.R"))
source(here("stan_utility.R"))
source(here("read.admb.R"))

# Read in report file

repFilePath <- file.path(params$rootDir, params$RdataFile)
reports     <- readRDS(repFilePath)

repObj <- c(reports$repOpt, reports$data)
repObj <- renameReportArrays(repObj = repObj, datObj = reports$data )
repObj <- calcRefPts(repObj)
reports$repOpt <- repObj

fYear   <- reports$fYear
lYear   <- reports$lYear
nP      <- repObj$nP
nT      <- repObj$nT
nG      <- repObj$nG
nLenX   <- repObj$nLenX

calcSD <- reports$ctlList$ctrl$calcSD
gradTable <- reports$grad

fitReport <- reports$fitReport
nPhase    <- nrow(fitReport)-1

isPosts <- !is.null(reports$posts)
isStan  <- !is.null(reports$stanfit)


gearLabs  <- reports$gearLabs
stockLabs <- reports$stock
species   <- reports$ctlList$ctrl$speciesName
sexLabs   <- dimnames(reports$data$L_lxpgt)[[2]]

gearComm <- 1:nG

nonfiniteSEs  <- !is.finite(gradTable[,2])
nanSEs        <- is.nan(gradTable[,2])

# Read ISCAM rep file
SCALrep <- lisread(here("Data",params$prevRep))

# sink(here("output.txt"))
# browser()

```

Standard fit report for fits of SISCAL to `r species` data.

Data Scenario: `r reports$ctlList$ctrl$dataScenarioName`

Model Hypothesis: `r reports$ctlList$ctrl$modelHypName`

Species: `r reports$ctlList$data$species`

Stocks: `r reports$ctlList$data$stocks`

## Final phase convergence diagnostics

Max Gradient: `r fitReport[nPhase,]$maxGrad`

Objective Function value: `r fitReport[nPhase,]$objFun`

Time to fit model:  `r round(sum(fitReport[1:nPhase,"time"],na.rm = T),2)`

PD Hessian: `r ifelse( calcSD, reports$sdrepOpt$pdHess, calcSD)`

No. of Non-finite SEs: `r sum((nonfiniteSEs |nanSEs))`



```{r, captions, include = FALSE, echo = FALSE}
SBtRtMtFtCaption <- paste("Time series of spawning biomass with scaled spawn indices (top),
recruitments (second row), and harvest rates (bottom row) for 
substocks of ", species, ". Catch bars in the harvest rate plot show landings only (not releases).", sep = "")

allBioCap <- "Posterior mean and 95\\% credibility intervals of legal (<81cm) and spawning biomass, and posterior mean total Atlantic Halibut biomass. The vertical dashed line shows 1988, the first year where fish below 81cm were discarded in the long-line fleets."

idxFitsCap <- "Model fits to abundance and biomass indices, with standardised log residuals for each index (bottom panel)."

AgeDataFitCap <- "Time-averaged model fits to length composition data. Sexes/stocks are left to right, 
and gears are top to bottom."

AggAgeDataFitCap <- "Model fits to age data, averaged over stock and time. Gears are top to bottom."
# SBsptCaption <- "Spawning biomass (red line), catch (grey bars), and scaled biomass indices (coloured points), for all stocks and species. Indices are scaled by the fleet catchability, then by the ratio of spawning biomass to vulnerable biomass."

# StdIdxCap   <- "Standardised vulnerable biomass (coloured lines) and the scaled and standardised biomass indices they are fitting to (coloured points), for all stocks and species."

# IdxResCap   <- "Standardised residuals for model fits to biomass indices (coloured points) and a loess smoother with a 20% confidence interval (coloured lines and grey regions), for all fleets, stocks, and species."

RecPlotCap <- "Age-1 recruitments for all stocks. Equilibrium unfished recruitment $R_0$ is 
indicated by the horizontal dashed line. Second row shows recruitment residuals on the log scale, 
with the average of estimated residuals shown by the horizontal red dashed line."

# RecDevPlotCap <- "Deviations from expected recruitment for all species and stocks."

refPtsUcap <- "Equilibrium yield (top) and biomass (bottom) curves as a function of total legal harvest rates. $U_{MSY}$ reference points are shown as closed circles on each line. Posterior 95\\% credibility intervals in yield and biomass are shown as envelopes, while the 95\\% credibility interval for legal $U_{MSY}$ is shown by the vertical dashed lines."

kobePlotCap <- "Phase plot showing spawning biomass (vertical axis) and total legal harvest rate (horizontal axis) relative to $U_{MSY}$ reference points. Arrows show the direction of time, beginning in 1970 and ending in 2020. Equilibrium spawning biomass is shown as a faint grey curve in the background of the plot."

# ProbLenAgeCap <- "Probability curves of length-at-age for males (blue) and females (red). Curves show the probability of each length within an age group, and opacity of the lines increases with age."

# tvqCap <- "Time series of observation model catchability (log-scale, coloured points) for the commercial fleets and Hecate Strait Multispecies Assemblage survey. Lines show the smoothed trend using a Loess smoother"

# fishingMortCap <- "Estimates of fishing mortality from each fleet (coloured points and lines), gridded over species (columns) and stocks (rows). Fishing mortality rates are found using an iterative Newton-Rhapson solver conditioned on the observed catch."

SRplotCap <- "Stock-recruit curves (solid lines) and modeled recruitments (coloured points)"

selAgeCap <- "Selectivity-at-age for each fleet (rows), and sex (columns)."
selLenCap <- "Selectivity-at-length for each fleet (rows)."

catchBarCap <- "Catch (landings and releases) in biomass units, with colours corresponding to commercial fleets."

relCap <- "Total releases in biomass units by fleet."

divCaption <- "Trace plots of parameters with $\\hat{R} > 1.5$ showing divergences."

dataObjFunCap <- "Objective function components for data observations."

stdPriorObjFunCap <- "Objective function components for standard (single level) and hyper-priors."

hierPriorObjFunCap <- "Objective function components for hierarchical (mult-level) priors."

sdRepCap  <- "SD report showing leading parameter estimates, standard errors, 
gradient components, and coefficients of variation. Gradients with a magnitude
above 1e-3 are shown in bold red, while the coefficients of variation (cv) are  
coloured so that smaller values are lighter in colour, and larger values 
are darker, with cvs above .5 in bold, and cvs above 3 in red."

lenDataCVtabCap <- "Estimated standard deviations for length composition data
series."

otherDataCVtabCap <- "Estimated standard deviations for proportion females
observed in the length composition data (first 6 columns), and survey indices
of Atlantic Halibut (last two columns)."

deltaLNprobsCap <- "Probability of detection of a spawning event,
with respect to spawning stock biomass. Lines show the modeled probability
and the points indicate whether a spawn was detected, with 0 
for no spawn detected, and 1 for a positive index."

compCorrMtxCap <- character(length = 3)
for( gIdx in 1:nG)
  compCorrMtxCap[gIdx] <- paste( "Estimated correlation matrices for age composition residuals in the ",
                                 gearLabs[gIdx], " fleet. The circles above the visualise the numbers below the diagonal.")

```


# Model fits

## At-a-glance

```{r, AtAGlance, echo = FALSE, message = FALSE, fig.cap = SBtRtMtFtCaption }
plotMulti(ts = c("SBtIdx","Rt","Ftg"), repList = reports)
```

```{r, allBio, echo = FALSE, message = FALSE, fig.cap = allBioCap }
plotTotLegalB(repList = reports)
```


## Fits to data

```{r, idxFits, echo = FALSE, fig.cap = idxFitsCap }
plotIdxFits( repList = reports )
```



```{r deltaLNProbs, echo = FALSE, fig.cap = deltaLNprobsCap}
# plotDeltaLNFits( reports = reports )
```

```{r, lenDataFits, echo = FALSE, fig.cap = AgeDataFitCap }

plotLengthFitAvg(  repList = reports )

```

```{r, ageDataFitsAvg, echo = FALSE, fig.cap = AggAgeDataFitCap }

# plotAgeFitAggAvg( repList = reports)

```



```{r dataCVtables, echo = FALSE }

# Pull age obs error and survey obs errors
tauLen_xpg  <- sqrt( repObj$tau2Len_xpg[,,1:6,drop = FALSE] )
tauSurv_pg  <- repObj$tauObs_pg[,5:6,drop = FALSE]
tauPropF_pg <- sqrt( repObj$tau2PropF_pg )

# Make the table
lenDataCVtab <- matrix(NA, nrow = nLenX, ncol = 6 )
rownames( lenDataCVtab ) <- sexLabs
colnames( lenDataCVtab ) <- c( "$\\tau^{len}_{LLNAFO3}$",
                            "$\\tau^{len}_{LLNAFO4}$",
                            "$\\tau^{len}_{OTNAFO3}$",
                            "$\\tau^{len}_{OTNAFO4}$",
                            "$\\tau^{len}_{RV}$",
                            "$\\tau^{len}_{HS}$" )

lenDataCVtab <- as.data.frame(lenDataCVtab)
lenDataCVtab[,1] <- round(tauLen_xpg[,1,1],3)
lenDataCVtab[,2] <- round(tauLen_xpg[,1,2],3)
lenDataCVtab[,3] <- round(tauLen_xpg[,1,3],3)
lenDataCVtab[,4] <- round(tauLen_xpg[,1,4],3)
lenDataCVtab[,5] <- round(tauLen_xpg[,1,5],3)
lenDataCVtab[,6] <- round(tauLen_xpg[,1,6],3)

kable(  lenDataCVtab, escape = FALSE, 
        caption = lenDataCVtabCap, booktabs = T,
        align = rep("c",ncol(lenDataCVtab))) %>%
  kable_styling(latex_options = c("striped", "scale_down","hold_position"),
                bootstrap_options = c("striped", "hover"))

otherDataCVtab <- matrix(NA, nrow = 8, ncol = nP )
colnames(otherDataCVtab) <- stockLabs
rownames(otherDataCVtab) <- c(  "$\\tau^{propF}_{LLNAFO3}$",
                                "$\\tau^{propF}_{LLNAFO4}$",
                                "$\\tau^{propF}_{OTNAFO3}$",
                                "$\\tau^{propF}_{OTNAFO4}$",
                                "$\\tau^{propF}_{RV}$",
                                "$\\tau^{propF}_{HS}$",
                                "$\\tau^{surv}_{RV}$",
                                "$\\tau^{surv}_{HS}$"   )

otherDataCVtab[1,] <- round(tauPropF_pg[,1],3)
otherDataCVtab[2,] <- round(tauPropF_pg[,2],3)
otherDataCVtab[3,] <- round(tauPropF_pg[,3],3)
otherDataCVtab[4,] <- round(tauPropF_pg[,4],3)
otherDataCVtab[5,] <- round(tauPropF_pg[,5],3)
otherDataCVtab[6,] <- round(tauPropF_pg[,6],3)
otherDataCVtab[7,] <- round(tauSurv_pg[,1],3)
otherDataCVtab[8,] <- round(tauSurv_pg[,2],3)

kable(  otherDataCVtab, escape = FALSE, 
        caption = otherDataCVtabCap, booktabs = T,
        align = rep("c",ncol(otherDataCVtab))) %>%
  kable_styling(latex_options = c("striped", "scale_down","hold_position"),
                bootstrap_options = c("striped", "hover"))
```

## Recruitment

```{r, recruitments, echo = FALSE, fig.cap = RecPlotCap }
plotMulti(ts = c("Rt","RtResids"), repList = reports )
```


```{r, stockRecCurves, echo = FALSE, fig.cap = SRplotCap }
plotSR( repList = reports )
```

## Natural Mortality
```{r MtSeries, echo = FALSE, fig.cap = "Mt"}
plotMulti(ts = "Mt", repList = reports)
```

```{r ddM, echo = FALSE, fig.cap = "densityDependent M"}
# plotDDmort(repObj = reports$repOpt)
```

```{r natMortAtAge, fig.cap = "Total natural mortality at age"}
# plotNatMortAtAge( repList = reports,
#                   nCols = 2,
#                   pIdx = 1)
```

```{r totMortAtAge, fig.cap = "Total mortality at age"}
# plotTotMortAtAge( repList = reports,
#                   nCols = 2,
#                   pIdx = 1 )
```

## Selectivity and Catch

```{r, plotCatchBarsAllYrs, echo = FALSE, fig.cap = catchBarCap }
plotC_pgt( repList = reports)
```


```{r, plotRelCatch, echo = FALSE, fig.cap = relCap }
plotRelCatch(reports ) 
```


```{r, plotSelAge, echo = FALSE, fig.cap = selAgeCap }
plotSag(repList = reports, fleets = gearComm )
```

```{r, plotSelLen, echo = FALSE, fig.cap = selLenCap }
plotSlg(repList = reports )
```


```{r, plotProbRelease, echo = FALSE, fig.cap = "Release prob"}
plotProbRelease(reports)
```

```{r, plotProbLenAge, echo = FALSE, fig.cap = "Length-at-age distributions"}
plotProbLenAge(reports)
```

## Reference Points


```{r, refPtsU, fig.cap = refPtsUcap, echo = FALSE, include = TRUE}

plotRefPtsU( reports,
              pIdx = 1)


```

```{r, kobePhase, fig.cap = kobePlotCap, echo = FALSE, include = TRUE}

plotKobePhase(  reports,
                pIdx = 1)


```

# Stock specific fits

```{r, StockChild, echo = FALSE, message = FALSE, results = "asis" }
for( p in 1:nP)
{
  cat(paste("## ", stockLabs[p], "\n",sep = "")) 

  childDoc <- knitr::knit_child(here::here("Documentation","stockChild.Rmd"),options = list(results = "asis"),quiet = TRUE)

  cat(childDoc)
}

```

# Optimisation performance

## Objective function components
```{r objFunCpts, echo = FALSE, include = FALSE}

# Pull objective function components
objFun            <- reports$repOpt$objFun
obsIdxNLL_pg      <- reports$repOpt$obsIdxNLL_pg
ageObsNLL_pg      <- reports$repOpt$ageObsNLL_pg
lenObsNLL_xpg     <- reports$repOpt$lenObsNLL_xpg

mort_nlp          <- reports$repOpt$mort_nlp
Mdev_nlp          <- reports$repOpt$Mdev_nlp
tvMnlp_p          <- reports$repOpt$tvMnlp_p
rec_nlp           <- reports$repOpt$rec_nlp
init_nlp          <- reports$repOpt$init_nlp
h_nlp             <- reports$repOpt$h_nlp
hDev_nlp          <- reports$repOpt$hDev_nlp
nlptau2idx_pg     <- reports$repOpt$nlptau2idx_pg
nlptau2idx_g      <- reports$repOpt$nlptau2idx_g

tvselAlphaDevNLP  <- reports$repOpt$tvselAlphaDevNLP
tvselBetaDevNLP   <- reports$repOpt$tvselBetaDevNLP
selAlphaDevNLP_pg <- reports$repOpt$selAlphaDevNLP_pg
selBetaDevNLP_pg  <- reports$repOpt$selBetaDevNLP_pg
selAlphaNLP_g     <- reports$repOpt$selAlphaNLP_g
selBetaNLP_g      <- reports$repOpt$selBetaNLP_g
obsMixedIdxNLL_g  <- reports$repOpt$obsMixedIdxNLL_g
ageObsNLL_g       <- reports$repOpt$ageObsNLL_g
lnB0_p            <- log(reports$repOpt$B0_p) 
psi_nlp           <- reports$repOpt$psi_nlp
```

```{r dataObjFun, echo = FALSE}
dataColNames <- c(  "objFun",
                    "obsRV",
                    "obsHS",
                    "lenLL_NAFO3",
                    "lenLL_NAFO4",
                    "lenOT_NAFO3",
                    "lenOT_NAFO4",
                    "lenRV_4VWX",
                    "lenHS_f",
                    "lenHS_r" )

dataRowNames <- c(  "Total", sexLabs )

obs5Tot <- c( sum( obsIdxNLL_pg[,5] ), rep(NA,nLenX))
obs6Tot <- c( sum( obsIdxNLL_pg[,6] ), rep(NA,nLenX))
len1Tot <- c( sum( lenObsNLL_xpg[,1,1] ), lenObsNLL_xpg[,1,1])
len2Tot <- c( sum( lenObsNLL_xpg[,1,2] ), lenObsNLL_xpg[,1,2])
len3Tot <- c( sum( lenObsNLL_xpg[,1,3] ), lenObsNLL_xpg[,1,3])
len4Tot <- c( sum( lenObsNLL_xpg[,1,4] ), lenObsNLL_xpg[,1,4])
len5Tot <- c( sum( lenObsNLL_xpg[,1,5] ), lenObsNLL_xpg[,1,5])
len6Tot <- c( sum( lenObsNLL_xpg[,1,6] ), lenObsNLL_xpg[,1,6])
len7Tot <- c( sum( lenObsNLL_xpg[,1,7] ), lenObsNLL_xpg[,1,7])

dataObjFunTab <- matrix( NA, nrow = 1 + length(sexLabs), 
                             ncol = length(dataColNames))
colnames(dataObjFunTab) <- dataColNames
rownames(dataObjFunTab) <- dataRowNames

dataObjFunTab <- as.data.frame(dataObjFunTab)

# Fill
dataObjFunTab$objFun      <- round(objFun,2)
dataObjFunTab$obsRV       <- round(obs5Tot,2)
dataObjFunTab$obsHS       <- round(obs6Tot,2)
dataObjFunTab$lenLL_NAFO3 <- round(len1Tot,2)
dataObjFunTab$lenLL_NAFO4 <- round(len2Tot,2)
dataObjFunTab$lenOT_NAFO3 <- round(len3Tot,2)
dataObjFunTab$lenOT_NAFO4 <- round(len4Tot,2)
dataObjFunTab$lenRV_4VWX  <- round(len5Tot,2)
dataObjFunTab$lenHS_f     <- round(len6Tot,2)
dataObjFunTab$lenHS_r     <- round(len7Tot,2)


kable(  dataObjFunTab, escape = FALSE, 
        caption = dataObjFunCap, booktabs = T,
        align = rep("c",ncol(dataObjFunTab))) %>%
  kable_styling(latex_options = c("striped", "scale_down","hold_position"),
                bootstrap_options = c("striped", "hover"))
```


```{r stdPriorObjFunTab, echo = FALSE }


stdPriorColNames <- c(  "objFun",
                        "recDevs",
                        "initDevs",
                        "h",
                        "M",
                        "tvMdev",
                        "IGtau_surf",
                        "IGtau_dive",
                        "tvSelAlpha",
                        "tvSelBeta",
                        "selAlphaRed",
                        "selAlphaSR",
                        "selAlphaGn",
                        "selBetaRed",
                        "selBetaSR",
                        "selBetaGn",
                        "lnB0",
                        "lnRinit",
                        "psiSOK" )




                        

stdPriorObjFunTab <- matrix( NA, nrow = length(stdPriorColNames), ncol = 1)
rownames(stdPriorObjFunTab) <- stdPriorColNames
stdPriorObjFunTab <- as.data.frame(stdPriorObjFunTab)

stdPriorObjFunTab["objFun",1]        <- round(objFun,2)
stdPriorObjFunTab["recDevs",1]       <- round(rec_nlp,2)
stdPriorObjFunTab["initDevs",1]      <- round(init_nlp,2)
stdPriorObjFunTab["h",1]             <- round(h_nlp,2)
stdPriorObjFunTab["M",1]             <- round(mort_nlp,2)
stdPriorObjFunTab["tvMdev",1]        <- round(sum(tvMnlp_p),2)
stdPriorObjFunTab["psiSOK",1]        <- round(psi_nlp,2)
stdPriorObjFunTab["IGtau_surf",1]    <- round( sum(nlptau2idx_pg[,4]),2)
stdPriorObjFunTab["IGtau_dive",1]    <- round( sum(nlptau2idx_pg[,5]),2)
stdPriorObjFunTab["tvSelAlpha",1]    <- round(tvselAlphaDevNLP,2)
stdPriorObjFunTab["tvSelBeta",1]     <- round(tvselBetaDevNLP,2)
stdPriorObjFunTab["selAlphaRed",1]   <- round(sum(selAlphaNLP_g[1]),2)
stdPriorObjFunTab["selAlphaSR",1]    <- round(sum(selAlphaNLP_g[1]),2)
stdPriorObjFunTab["selAlphaGn",1]    <- round(sum(selAlphaNLP_g[3]),2)
stdPriorObjFunTab["selBetaRed",1]    <- round(sum(selBetaNLP_g[1]),2)
stdPriorObjFunTab["selBetaSR",1]     <- round(sum(selBetaNLP_g[1]),2)
stdPriorObjFunTab["selBetaGn",1]     <- round(sum(selBetaNLP_g[3]),2)
stdPriorObjFunTab["lnB0",1]          <- sum(log(reports$repOpt$B0_p))
stdPriorObjFunTab["lnRinit",1]       <- sum(log(reports$repOpt$Rinit_p))



kable(  stdPriorObjFunTab, escape = FALSE, 
        caption = stdPriorObjFunCap, booktabs = T,
        align = rep("c",ncol(stdPriorObjFunTab))) %>%
  kable_styling(latex_options = c("striped", "scale_down","hold_position"),
                bootstrap_options = c("striped", "hover"))

```

```{r hierPriorObjFunTab, echo = FALSE, eval=FALSE }

hierPriorColNames <- c( "objFun",
                        "MDev",
                        "hDev",
                        "selAlphaDevR",
                        "selAlphaDevSR",
                        "selAlphaDevGn",
                        "selBetaDevR",
                        "selBetaDevSR",
                        "selBetaDevGn" )

hierPriorObjFunTab <- matrix( NA, ncol = 1, nrow = length(hierPriorColNames))
rownames(hierPriorObjFunTab) <- hierPriorColNames
hierPriorObjFunTab <- as.data.frame(hierPriorObjFunTab)


hierPriorObjFunTab["objFun",1]           <- round(objFun,2)   
hierPriorObjFunTab["MDev",1]             <- round(Mdev_nlp,2)
hierPriorObjFunTab["hDev",1]             <- round(hDev_nlp,2)
hierPriorObjFunTab["selAlphaDevR",1]     <- round(sum(selAlphaDevNLP_pg[,1]),2)
hierPriorObjFunTab["selAlphaDevSR",1]    <- round(sum(selAlphaDevNLP_pg[,2]),2)
hierPriorObjFunTab["selAlphaDevGn",1]    <- round(sum(selAlphaDevNLP_pg[,3]),2)
hierPriorObjFunTab["selBetaDevR",1]      <- round(sum(selBetaDevNLP_pg[,1]),2)
hierPriorObjFunTab["selBetaDevSR",1]     <- round(sum(selBetaDevNLP_pg[,2]),2)
hierPriorObjFunTab["selBetaDevGn",1]     <- round(sum(selBetaDevNLP_pg[,3]),2)





kable(  hierPriorObjFunTab, escape = FALSE, 
        caption = hierPriorObjFunCap, booktabs = T,
        align = rep("c",ncol(hierPriorObjFunTab))) %>%
  kable_styling(latex_options = c("striped", "scale_down","hold_position"),
                bootstrap_options = c("striped", "hover"))
```

## Phase fit table

```{r, phaseTable, echo = FALSE }
phaseReportTable <- reports$fitReport

kable(  phaseReportTable, escape = FALSE, 
        caption = "Optimisation performance of SISCAL for each phase.", booktabs = T,
        align = rep("c",ncol(phaseReportTable))) %>%
  kable_styling(latex_options = c("striped", "scale_down","hold_position"),
                bootstrap_options = c("striped", "hover"))

```


## Leading Parameter SDReport
```{r gradTable, echo = FALSE }
gradTable <- reports$grad 

parnames <- rownames(gradTable)
maxCV <- max(gradTable$cv, na.rm = T)

gradTable <- gradTable %>%
              mutate( 
                est = round(est, 4),
                se = round(se, 4),
                gr = signif(gr,2),
                cv = round(cv,4),
                gr =  ifelse( is.finite(gr),
                        cell_spec(  x = gr, format = "html",
                                    bold = ifelse( abs(gr) > 1e-3, TRUE, FALSE),
                                    color = ifelse( abs(gr) > 1e-3, "red", "black") ),
                        cell_spec( x = gr, format = "html",
                                    bold = TRUE, color = "red") ),
                cv =  ifelse( is.finite(cv),
                        ifelse( cv > 3,
                          cell_spec( x = cv, format = "html",
                                      color = "red", bold = TRUE),
                          cell_spec(  x = cv, format = "html",
                                      color = spec_color( cv, 
                                                          begin = .75, 
                                                          end = .25,
                                                          direction = 1,
                                                          na_color = "red",
                                                          option = "magma" ),
                                      bold = cv > .5 )
                                ),
                        cell_spec(  x = cv, format = "html",
                                    color = "red", bold = TRUE) ) )

                      

rownames(gradTable) <- parnames

kable(  gradTable, escape = FALSE, 
        caption = sdRepCap, booktabs = T,
        align = rep("c",ncol(gradTable))) %>%
  kable_styling(latex_options = c("striped", "scale_down","hold_position"),
                bootstrap_options = c("striped", "hover"))


```

# MCMC posteriors

## MCMC performance

```{r MCMCdiags, echo = FALSE, warning = FALSE, eval = isStan, fig.cap = "MCMC diagnostics plot."}
plotMCdiagnostics( reports )

```

## Prior/Posterior comparison

```{r steepPriorPost, echo = FALSE, warning = FALSE, eval = isPosts, fig.cap = "Prior (line) and posterior (bars) density of stock-recruit steepness."}
plotPriorPosteriorSteep( reports )
```

```{r mortPriorPost, echo = FALSE, warning = FALSE, eval = isPosts, fig.cap = "Prior (line) and posterior (bars) density of initial M (top) and time-averaged M (bottom) for males (blue) and females (red)."}
plotPriorPosteriorM( reports )
```


# Other

## Compositional Likelihood Correlation Matrices

```{r compCorrMtx, echo = FALSE, fig.cap = compCorrMtxCap[1:3], eval = FALSE}

for( g in 1:3 )
{
  Corr <- repObj$Corr_gaa[g,,]
  corrplot.mixed( Corr, lower.col = "black", number.cex = .7 )
}

```


# Comparisons with SCAL

```{r, SCALcaptions, include = FALSE, echo = FALSE}

compareAgeCompsCap <- "Plots of average age composition fits at the major stock level. Left is SISCA, right is ISCAM."

compareSBRtCap   <- "Comparison of spawning stock biomass and age-1 recruitment at the major stock level between SCAL and SISCAL-AH."



```

```{r BtRtComparison, echo = FALSE, fig.cap = compareSBRtCap}

plotBtRtComparison( repObj      = repObj,
                    datObj      = reports$data,  
                    prevRep     = SCALrep,
                    fYearSISCA  = fYear,
                    lYearSISCA  = lYear)


```

```{r plotCompSel, echo = FALSE, fig.cap = compareSBRtCap}

plotSelComparison(  repObj      = repObj,
                    prevRep     = SCALrep )


```


